MONID

### 2023-09-11 Paper/main.tex
update

\subsection{Relationship to LTL+P}
According to~\cite{barringer2004rule,barringer2003eagle}, we can define both \textbf{Future Time LTL} and \textbf{Past Time LTL} operators. The future modalities are written in section~\ref{sec:ltl}, therefore let us list the past ones:
\begin{align*}
    & \underline{\text{min}}\ \mathtt{Previous}(\underline{\text{Form}}\ F) = \odot F \\
    & \underline{\text{max}}\ \mathtt{AlwaysInPast}(\underline{\text{Form}}\ F) = F \land \odot \mathtt{AlwaysInPast}(F) \\
    & \underline{\text{min}}\ \mathtt{EventuallyInPast}(\underline{\text{Form}}\ F) = F \lor \odot \mathtt{EventuallyInPast}(F) \\
    & \underline{\text{min}}\ \mathtt{Since}(\underline{\text{Form}}\ F_1, \underline{\text{Form}}\ F_2) = F_2 \lor (F_1 \land \odot \mathtt{Since}(F_1,F_2))
\end{align*}
By combining the definitions for the future and past time LTLs defined above, we obtain a temporal logic over the future, present and past, in which one can freely intermix the future and past time modalities; thus, we can state that EAGLE is expressive at least as LTL+P.
% a differenza di ltl non salva tutta la sequenza ma solo una formula che riassume tutto. La seconda componente non è uno stato (insieme di cose vere) ma un record

>>>>

\subsection{Relationship to LTL+P}
According to~\cite{barringer2004rule,barringer2003eagle}, we can define both \textbf{Future Time LTL} and \textbf{Past Time LTL} operators. The future modalities are written in section~\ref{sec:ltl}, therefore let us list the past ones:
\begin{align*}
    & \underline{\text{min}}\ \mathtt{Previous}(\underline{\text{Form}}\ F) = \odot F \\
    & \underline{\text{max}}\ \mathtt{AlwaysInPast}(\underline{\text{Form}}\ F) = F \land \odot \mathtt{AlwaysInPast}(F) \\
    & \underline{\text{min}}\ \mathtt{EventuallyInPast}(\underline{\text{Form}}\ F) = F \lor \odot \mathtt{EventuallyInPast}(F) \\
    & \underline{\text{min}}\ \mathtt{Since}(\underline{\text{Form}}\ F_1, \underline{\text{Form}}\ F_2) = F_2 \lor (F_1 \land \odot \mathtt{Since}(F_1,F_2))
\end{align*}
By combining the definitions for the future and past time LTL as defined above, we obtain a temporal logic over the future, present and past, in which one can freely intermix the future and past time modalities; thus, we can state that EAGLE is expressive at least as LTL+P.
% a differenza di ltl non salva tutta la sequenza ma solo una formula che riassume tutto. La seconda componente non è uno stato (insieme di cose vere) ma un record

### 2023-09-11 Presentation/presentation.tex
update

>>>>

\begin{frame}{Relationship with LTL+P}
    We can define both \textbf{Future Time LTL} and \textbf{Past Time LTL} operators. As example, let us show the future ones.
    \begin{align*}
        & \underline{\text{min}}\ \mathtt{Next}(\underline{\text{Form}}\ F) = \bigcirc F \\
        & \underline{\text{max}}\ \mathtt{Always}(\underline{\text{Form}}\ F) = F \land \bigcirc \mathtt{Always}(F) \\
        & \underline{\text{min}}\ \mathtt{Eventually}(\underline{\text{Form}}\ F) = F \lor \bigcirc \mathtt{Eventually}(F) \\
        & \underline{\text{min}}\ \mathtt{Until}(\underline{\text{Form}}\ F_1, \underline{\text{Form}}\ F_2) = F_2 \lor (F_1 \land \bigcirc \mathtt{Until}(F_1,F_2))
    \end{align*}
    By combining the definitions for the future and past time LTL as defined above, we obtain a temporal logic over the future, present and past, in which one can freely intermix the future and past time modalities; thus, we can state that EAGLE is expressive at least as LTL+P.
